%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage{helvet}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge\bf{\href{https://www.linkedin.com/in/sharathguna/}{G SHARATH}}
\end{center}
\vspace{-7mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-9mm}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:mailtosharath002@gmail.com}{mailtosharath002@gmail.com} ~\textbullet~ \(+91\) 9535936032 ~\textbullet~ \ Bangalore, India ~\textbullet~ \href{https://www.linkedin.com/in/sharathguna/}{linkedin : sharathguna}
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{B.E in Computer Science and Engineering } \hfill 2014 - 2018 \\
\href{http://pesitsouth.pes.edu/}{  PES Institute Of Technology, South Campus , Bangalore, India}
\begin{itemize}
 \item Aggregate of 75.4\% as of Final Year
\end{itemize}
\textbf{High School} - {SBM Jain College, Bangalore} (PUC) - 90.5\% \hfill 2012 - 2014 \\
\textbf{Secondary School} - St. Mira's High School (ICSE) - 83.9\% \hfill 2000 - 2012
%----------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%---------------------------------------------------------------------------------------

\section{Publications}
\begin{itemize}[leftmargin=*]
\item  \textbf{Sharath Guna}, ``The Evolution of Video Codecs and the Future'', RISE 2017, 3rd National Conference on "Recent Innovations in Science and Engineering", May 6$^{th}$, 2017 , Bangalore. \href{https://www.ijsr.net/conf/RISE2017/IJSR10.pdf}{View}
\end{itemize}


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Strongest Areas} - Algorithms, Image Processing, Data Structures \\
\textbf{Languages} - Java, C, C++, Python, PHP, SQL, JS\\
\textbf{Tools/Frameworks} - MySQL, SQLite, OpenCV,\LaTeX, OpenGL , Android .


%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Projects}
All projects available on git : \url{https://github.com/sharathguna}
%\setlist[itemize]{
\begin{itemize}[leftmargin=*]
 \item \textbf{{Face Authorization Surveillance }} : Built a system app that detects and recognizes
multiple authorized persons in real-time by employing the Eigen Faces algorithm using the HAAR Cascade Classifiers.

\item \textbf{{Accident Prevention for Influenced }}: Worked as a team of 4 for building the afore mentioned
prototype which detects unusual driver's head movements and captures iris data to send warning signal to the microcontroller.

\item \textbf{{Custom UNIX Shell}} : Developed an Unix shell with custom commands by creating an own parser that parses and tokenizes the input and performs specific operations.

\item \textbf{{Young's Double Slit Simulation }}: A Mini-project that simulates the infamous Young's Double Slit Experiment using OpenGL and SOX .

\end{itemize}


%----------------------------------------------------------------------------------------
%	RELEVANT COURSE SECTION
%----------------------------------------------------------------------------------------
\section{Relevant \hspace{2mm} Courses}
Data Structures and Algorithms, Machine Learning and Pattern Recognition,Artificial Intelligence,Discrete Mathematics, Operating System, Computer Graphics, Unix Programming, Advance Computer Networks, Databases, Theory Of Computation and Automata, Software Engineering.
%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------

\section{Achievements and Awards}
\begin{itemize}[leftmargin=*]
 \item 6th International Olympiad Of Mathematics 2013. (State rank : 110 )
 \item Bagged Second Prize in ''Debug IT'' Intercollegiate Debugging Competition, Nov 2013.
 \item Selected for Top 5 amongst 120 Teams in KLUDGE 24-Hour Hackathon, Apr 2017.
 \item Secured First Prize in Senior Category at school level - Titan Genius Kidz National
Arithmetic Championship 2009.
 \item Secured 7th (Top 10) in Computer Science in India - QuizUp, Sept 2016.
\end{itemize}

%----------------------------------------------------------------------------------------
\section{Hackathons}
\begin{itemize}[leftmargin=*]
 \item InGENIUS 24Hr 2015 : Built an Aptitude Android App "Triviality". 
 \item CODE2k16 24 Hr 2016 : Presented the Face Authorization Project.
 \item init 12Hr 2016 : Built a Food Donate Android App "FeedTheNeed".
 \item KLUDGE 24 Hr 2017 : Presented the Accident Prevention Project. 
 \item MANTHAN, BIT 2016 : Built an Android App "GreenBen". 
 \item InGENIUS 24Hr 2017 : Built a Face Emotion Recognition App.
\end{itemize}

%	HOBBIES SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
Writing on \href{https://www.quora.com/profile/Sharath-Guna-1}{Quora}, Stock and Crypto Trading, Learning Cosmos, Trekking and Reading Classics.

\section{Strengths}
An Autodidact , Quick Grasper , Brisk Learner, Acclimatized and Adaptive Person, Good Team-worker.

\end{resume}
\end{document}